# How it Works

`te_parser::evaluate()` uses a simple recursive descent parser to compile your
expression into a syntax tree. For example, the expression `"sin x + 1/4"`
parses as:

```{r}
#| echo: false
#| out-width: 100%
#| fig-format: png

DiagrammeR::grViz("digraph {
  graph [layout = dot, rankdir = TB]
  
  node [shape = oval]        
  node1 [label = '+']
  node2 [label = 'sin']
  node3 [label =  'รท', style=filled, fillcolor = '#add8e6']
  node4 [label = 'x']
  node5 [label = '1', style=filled, fillcolor = '#add8e6']
  node6 [label = '4', style=filled, fillcolor = '#add8e6']
  
  # edge definitions with the node IDs
  node1 -> node2 -> node4
  node1 -> node3
  node3 -> node5
  node3 -> node6
  }")
```

`te_parser::evaluate()` also automatically prunes constant branches. In this example,
the compiled expression returned by `compile()` would become:

```{r}
#| echo: false
#| out-width: 100%
#| fig-format: png

DiagrammeR::grViz("digraph {
  graph [layout = dot, rankdir = TB]
  
  node [shape = oval]        
  node1 [label = '+']
  node2 [label = 'sin']
  node3 [label =  '0.25', style=filled, fillcolor = '#add8e6']
  node4 [label = 'x']

  # edge definitions with the node IDs
  node1 -> node2 -> node4
  node1 -> node3
  }")
```

## Grammar {-}

*TinyExpr++* parses the following grammar (from lowest-to-highest operator precedence):

    <list>      =    <expr> {(",", ";" [dependent on locale]) <expr>}
    <expr>      =    <term> {("&" | "|") <term>}
    <expr>      =    <term> {("<>" | "!=" | "=" | "<") | "<=") | ">" | ">=") <term>}
    <expr>      =    <term> {("<<" | ">>") <term>}
    <expr>      =    <term> {("+" | "-") <term>}
    <term>      =    <factor> {("*" | "/" | "%") <factor>}
    <factor>    =    <power> {("^" | "**") <power>}
    <power>     =    {("-" | "+")} <base>
    <base>      =    <constant>
                   | <variable>
                   | <function-0> {"(" ")"}
                   | <function-1> <power>
                   | <function-X> "(" <expr> {"," <expr>} ")"
                   | "(" <list> ")"
